The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
halfway edits hab sel perspective

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
the geographical range of a species, the home range of an individual, the habitat patches within the home range and specific resources within a
habitat patch. 
Moving past this hierarchical perspective, Mayor (2009) reviewed
types of scale relevant in measurement of habitat selection and recommend using
a continuum of scales for identifying characteristic scales of selection. 
<!-- highlight this -->A continuum of scales allows xyz advantage

For
example, @Mayor_2007 showed caribou select for shallow snow at all scales and <!--what else higlight-->
and by using a continuum of scales, avoided the bias of predefined scales assumed to be associated with certain behaviors.

<!-- Relationship between sociality and habitat -->
<!-- more from Webber, He, etc -->
<!-- Merkle’s memory and patches for bison (and leaders) -->
<!-- Emergent  Properties  of  Conspecific  Attraction  inFragmented  Landscapes-->
<!-- Conspecific Attraction and Aggregation in Territorial Species-->
<!-- Energy and the Scaling of Animal Space Use-->

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougar
home ranges overlapped more in regions with high hunting opportunity, a
proxy for resource richness [@Elbroch_2016]. Caribou sociality differed between seasons, where social associations were stronger in winter and contrastingly
low in summer when resource availability are more homogenous [@Peigner_2019]. Bison
(*Bison bison*) showed stronger habitat selection in larger groups and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. These examples, comparing sociality and habitat selection across temporal or spatial contexts, are implicitly multilayer analyses. <!--Despite these, *missing multilayer approach*.-->

>>>>

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
the geographical range of a species, the home range of an individual, the habitat patches within the home range and specific resources within a
habitat patch. <!-- examples of hierarchical hab sel Kie 2002-->
Moving past this hierarchical perspective, Mayor (2007) emphasized the importance of considering a broad continuum of scales to reveal scale-dependent selection and avoid the bias of predefined scales assumed to be associated with certain behaviors.

Then to Mayor 2009

<!-- And more recent? -->

Despite this, still not widely adopted McGarigal 2016

For
example, @Mayor_2007 showed caribou select for shallow snow at all scales 
and by using a continuum of scales, .

<!-- Relationship between sociality and habitat -->
<!-- Merkle’s memory and patches for bison (and leaders) -->
<!-- Emergent  Properties  of  Conspecific  Attraction  inFragmented  Landscapes-->
<!-- Conspecific Attraction and Aggregation in Territorial Species-->
<!-- Energy and the Scaling of Animal Space Use-->

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougar
(*Puma concolor*) home ranges overlapped more in regions with high hunting
opportunity, a proxy for resource richness [@Elbroch_2016]. Caribou (*Rangifer
tarandus*) sociality differed between seasons, where social associations were
stronger in winter and contrastingly low in summer when resource availability
are more homogenous [@Peigner_2019]. Bison (*Bison bison*) showed stronger
habitat selection in larger groups and avoidance of predation risk was a main
factor contributing to their habitat selection [@Fortin_2009]. These examples,
comparing sociality and habitat selection across temporal or spatial contexts,
are implicitly multilayer analyses.
